---
title: "HISCO classification"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{HISCO classification}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

A package for classifing HISCO codes (Historical International Standard Classification of Occupations) to HISCLASS, HISCLASS 5, SOCPO and Universal HISCAM historical socla class systems.

For further references see [HSN standardized, HISCO-coded and classified occupational titles, release 2013.01](http://www.iisg.nl/hsn/data/occupations.html)

## Examples

Getting the default, HISCLASS.

```{r}
library(hisco)
hisco_codes <- c(22670, 22675, 22680, 22690, 30000, 31000, 31020, 31030, 31040)
hisco_to_ses(hisco_codes)
```

SOCPO classification with status codes.

```{r}
hisco_to_ses(hisco_codes, "socpo", status = rep(33, length(hisco_codes)))
```

Classification to label HISCLASS.

```{r}
hisco_to_ses(hisco_codes, "hisclass", label = TRUE)
```

With summary statistics.

```{r}
hisco_to_ses(hisco_codes, messages = TRUE)
```



